### 2016-08-21 Engine.tex
继续撰写node split部分,本次提交为了测试ssh

Once the keys in a node share a common prefix, that prefix can be
removed from the keys and form a new single key node (since the prefix
is either a character or a string, the type of the new node is either
Map 4 or String Array). This technique can reduce a lot of redundant
comparisons while searching a target key in that node. For instance,
consider the node in Fig whose four keys share a common prefix $a^4$,
and a target key which is $a^4u$. it will be compared with the four
keys in order and finally takes $5 \times 4 = 20$ byte comparisons to
determine the inexistence of target key. However, if $a^4$ is split
out and form another new node as shown in Fig , for the same target,
only 8 byte comparisons (4 comparisons for $node_1$ and another 4
comparisons for $node_2$) is needed.

>>>>

Once the keys in a node share a common prefix, that prefix can be
removed from the keys and form a new single key node. This technique
can reduce a lot of redundant comparisons while searching a target key
in a node. For instance, consider searching a target key $a^5u$ in a
string array type node whose four keys share a common prefix $a^5$, as
shown in Fig . According to Algorithm \ref{alg:string array}, the
target key have to be compared sequentially with the four keys in the
node, which will totally takes $6 \times 4 = 24$ byte comparisons to
determine the inexistence of target key. However, if the common prefix
$a^5$ is split out and form another new node as shown in Fig , for the
same target, only 9 byte comparisons (5 comparisons for $node_1$ and
another 4 comparisons for $node_2$) are needed for
searching. Comparing with only one node, the two nodes can reduce 15
comparisons. Note that, since the prefix is either a character or a
string, the new node is either a Map 4 node or a String Array node.
